---
title: "R Notebook"
output: html_notebook
---

1.Read in the state_income_data.csv file using the appropriate function.

```{r}

library(readxl)
library(openxlsx)
library(readr)

state_income_data <- read_csv("data/state_income_data.csv")

```

```{r}
View(state_income_data)
```

2. How do you specify your own column names when using read_csv()?

```{r}

#  read_csv(x, col_names = ...)
```

3. Read in the cars.csv file and use the col_types() function to ensure you load in:

X1 as character
mpg, cyl, disp, hp as double
vs as logical

```{r}

```


```{r}

cars <- read_csv("data/cars.csv", 
                 col_types = cols(vs = col_logical())
                 )
cars

```


4. Read in the scotland.txt file using the appropriate function

```{r}

scotland <- read_delim("data/scotland.txt", skip = 1, delim = ";")
scotland
View(scotland)

```

5. How do you read text into a one element character vector?

```{r}



```

6. Read in the steam-200k-sample.csv file. Fix any problems you may encounter.

```{r}



```

7. Read in the historic_eu_payments.tsv file.

```{r}
historic_eu_payments <- read_tsv("data/historic_eu_payments.tsv")
historic_eu_payments
```

8. How do you read lines of text into a multi-element text vector?

```{r}

```


9. Read in the africa_health_data.dta file using the appropriate method.


```{r}

library(readr)
library(haven)

africa_health <- read_stata("data/africa_health_data.dta")
africa_health <- as_factor(africa_health)
africa_health
```


10. Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt

```{r}
library(jsonlite)

sample_json <- fromJSON("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")

sample_json

```


